---
title: "Replicates Count computation with RISingVIS"
author: 
  - name: Chiara Pavia
    affiliation: | 
     San Raffaele Telethon Institute for Gene Therapy - SR-Tiget, 
     Via Olgettina 60, 20132 Milano - Italia
    email: pavia.chiara@hsr.it, giuliapais1@gmail.com, calabria.andrea@hsr.it
output: 
  BiocStyle::html_document:
    self_contained: yes
    toc: true
    toc_float: true
    toc_depth: 2
    code_folding: show
date: "`r doc_date()`"
package: "`r pkg_ver('RISingVIS')`"
vignette: >
  %\VignetteIndexEntry{Replicates Count computation with RISingVIS}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Introduction

In this vignette we explain how to use the functions dedicated to the 
computation of the replicates count ratio. 

The **replicates count ratio** is computed as follows: 

$$
R = \frac{\sum{RepCount[CEMs]}}{\sum{RepCount[Samples]}}
$$

We assume that the replicates count for an IS really belonging to that sample 
will be higher (most likely, 3) with respect to the one of a sample 
for which that IS is an artifact. 

# Load data

First, create an appropriate matrix and association file. 
These files are designed manually but simulate real research data.

```{r setup}
library(RISingVIS)

data("association_file")
data("integration_matrix")
```

Once we have our data we can start computing ratios. 

# replicates_IS_count()

The function `replicates_IS_count()` counts the number of replicates for
each sample for each single IS in the matrix. 

```{r}
replicates_IS_count(association_file, integration_matrix)
```

# replicates_IS_ratio()

The function `replicates_IS_ratio()` computes the ratio of the replicates count
for all the shared IS, considering each single sample and all samples together.

```{r}
replicates_IS_ratio(association_file, integration_matrix)
```

# replicates_IS_ratio_byIS()

The function `replicates_IS_ratio_byIS()` computes the ratio for all shared 
integrations considering one IS at a time, again computing it against each 
sample and against all samples together.

```{r}
replicates_IS_ratio_byIS(association_file, integration_matrix)
```
