---
title: "Sequence Count computation with RISingVIS"
author: 
  - name: Chiara Pavia
    affiliation: | 
     San Raffaele Telethon Institute for Gene Therapy - SR-Tiget, 
     Via Olgettina 60, 20132 Milano - Italia
    email: pavia.chiara@hsr.it, giuliapais1@gmail.com, calabria.andrea@hsr.it
output: 
  BiocStyle::html_document:
    self_contained: yes
    toc: true
    toc_float: true
    toc_depth: 2
    code_folding: show
date: "`r doc_date()`"
package: "`r pkg_ver('RISingVIS')`"
vignette: >
  %\VignetteIndexEntry{Sequence Count computation with RISingVIS}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Introduction

In this vignette it will be explained how to use the functions dedicated to the 
computation of the sequence count ratio. 

The **sequence count ratio** is computed as follows: 

$$
R = \frac{\sum{SeqCount[CEMs]}}{\sum{SeqCount[Samples]}}
$$

We assume that the SeqCount of integrations actually belonging to a sample is 
much higher with respect to the SeqCount resulting from the sharing 
of the integration itself. 

# Load data

First, create an appropriate matrix and association file or import the
ones that are included in the package data (these files are designed manually 
to simulate real research data).

```{r setup}
library(RISingVIS)

data("association_file")
data("integration_matrix")
```

If the input files that you want to use are different from our standard ones 
(see [ISAnalytics](https://calabrialab.github.io/ISAnalytics/dev/index.html) 
for more information) it is fundamental that you set up the workflow 
though the dynamic vars that are available thanks to ISAnalytics. Take a look [here](https://calabrialab.github.io/ISAnalytics/dev/articles/workflow_start.html)
to know how to do so!

Once we have our data we can start computing ratios. 


# shared_control_known_IS_ratio()

The function `shared_control_known_IS_ratio()` computes the ratio for all the 
shared control known integration sites. 

It is mandatory to specify, when calling the function, the association file and
the integration matrix; others parameters can be tuned according to need: 
* **subject_col** (default is *SubjectID*): the name of the column 
in the association file that reports the name of the subject 
* **amp_col** (default is *CompleteAmplificationID*): the name of the column 
in the association file and in the matrix that reports the identifier for the
single amplification
* **value_col** (default is *Value*): the name of the column in the integration
matrix that reports the sequence count for that integration in that sample
* **ctrl** (default is *CEM37*): if not default, this parameter must be a named 
list containing the name of the control cell line and the list of known 
integration sites for that control line. Default control il CEM37, which known 
integration sites can be viewed by calling the function `known_CEM_IS()`

The reported ratio is computed considering all shared integration sites known 
to belong to the control(s), all samples and all controls together.

```{r}
shared_control_known_IS_ratio(association_file, integration_matrix)
```

# shared_other_IS_ratio()

The function `shared_other_IS_ratio()` computes the ratio for all the shared 
integrations not belonging to controls. 

Similarly to the previous function, association file and integration matrix are 
mandatory, while other parametered can be tuned at need.

The reported ratio is computed considering all shared integration sites known 
to belong to the control(s), all samples and all controls together.

```{r}
shared_other_IS_ratio(association_file, integration_matrix)
```

# shared_IS_ratio()

The function `shared_IS_ratio()` computes the ratio for all shared integration 
sites considering one sample at a time for the denominator and all samples 
together. 

Parameters are the same as before and can be tuned at need, with the 
exception for the association file and integration matrix which are mandatory. 

With the use of this function the ratio is reported for all shared integration 
sites together, but considering one single sample at a time, then all together,
and similarly one control at a time (if there are more than one) and then 
all controls together. 

```{r}
shared_IS_ratio(association_file, integration_matrix)
```

# shared_IS_ratio_byIS()

The function `shared_IS_ratio_byIS()` computes the ratio for all integration 
sites considering one IS at a time, against each sample and against all samples 
together. 

Parameters are the same as before and can be tuned at need, with the 
exception for the association file and integration matrix which are mandatory. 

In this function the ratio is reported considering each integration site, 
first against each single sample and considering each single control and then
considering all samples and all (eventual) controls. 

```{r}
shared_IS_ratio_byIS(association_file, integration_matrix)
```

